### 2014-10-19 Docs/getting_started/getting_started.tex
add new paper ref, add new test problem description

>>>>

\item {\tt test\_spherical} \\[-3mm]

This problem sets up an isentropically stratified star and stirs it up
with a random velocity field.  The low Mach number constraint is
replaced with the anelastic constraint (through
the \runparam{beta\_type} runtime parameter).  Analytically, under
these conditions, the density of the star should not change.  This
test problem was discussed in Maestro paper IV~\cite{lowMach4}.
